\section*{Abstract}
\addcontentsline{toc}{section}{Abstract}

Spotlight is a full-stack web platform built for the LAU Soft Skills 2026 event,
a student showcase that simultaneously runs three formats: business plan
pitches, TED-style talks, and mock interviews. The platform serves three
audiences in real time: a public audience that votes for its favourite entry,
a panel of judges that grades each entry against a five-criterion rubric, and
an event admin who controls what the audience sees as the show progresses.

The system combines an LRU caching layer, per-route rate limiting, server-sent
events for sub-second push updates, an HMAC-based proof-of-vote token, an
in-memory anomaly detector, an append-only audit log, and an LLM-assisted
``quick read'' panel powered by Anthropic's Claude API with prompt caching.
Together these features address the non-functional requirements expected of a
production system: security, scalability, reliability, maintainability,
availability, and efficiency.

This report walks through the requirements, architecture, data model, detailed
design, implementation, and verification of the platform. Where useful, code
excerpts, sequence diagrams, and entity-relationship diagrams accompany the
prose. The intent is for a reader to be able to reproduce the system from this
document and the linked source repository.

\vspace{1em}
\noindent\textbf{Keywords:} React, Express, Supabase, Server-Sent Events,
prompt caching, rate limiting, anomaly detection, audit logging.

\section*{Acknowledgements}
\addcontentsline{toc}{section}{Acknowledgements}

Thanks to the LAU Soft Skills team for offering a real production deadline as
a forcing function, to the open-source maintainers of React, Express,
Supabase, pino, and Recharts whose libraries make a project of this scope
possible by a single student, and to my supervisor for steering the
non-functional priorities of this work.
