\section{Non-Functional Properties}
\label{sec:nonfunc}

This section ties each non-functional requirement (Section~\ref{sec:requirements})
to the specific artefact in the codebase that delivers it, and discusses
the residual risk.

\subsection{Security}

\paragraph{Defence in depth.} Spotlight stacks five independent defences
on the most-exposed endpoint (anonymous voting). No single defence is
load-bearing; an attacker has to defeat all five.

\begin{enumerate}[leftmargin=*]
  \item \textbf{HTTP-level hardening.} Helmet sets a strict CSP,
        \texttt{Strict-Transport-Security}, \texttt{X-Content-Type-Options:
        nosniff}, \texttt{X-Frame-Options: DENY}, and friends.
  \item \textbf{Schema validation.} Zod rejects malformed payloads at the
        controller boundary. Numbers must be numbers; UUIDs must parse;
        scores must be in $[0, 5]$.
  \item \textbf{Rate limiting.} Per-IP limits on \texttt{/auth/login} and
        \texttt{/votes}; per-judge limit on \texttt{/grades}; coarse
        overall limit on \texttt{/api/}.
  \item \textbf{HMAC proof-of-presence.} \texttt{/votes/init} issues a
        signed token bound to the browser token; \texttt{/votes} requires
        it.
  \item \textbf{Anomaly scoring.} Bursts and reuse patterns surface
        themselves into \texttt{vote\_flags}; high-severity rows are
        excluded from People's Choice.
\end{enumerate}

\paragraph{Identity \& secrets.} JWTs are signed with
\texttt{JWT\_SECRET} and expire in 7\,days. Passwords are bcrypt-hashed
with cost 10. \texttt{.env} files are git-ignored; \texttt{.env.example}
ships with names but no values. The Supabase service-role key never
leaves the backend.

\paragraph{SQL injection.} Every database call goes through the Supabase
JS client, which uses parameterised queries; no string concatenation
into a SQL fragment occurs anywhere in the codebase.

\paragraph{XSS.} React escapes interpolated values by default; we never
use \texttt{dangerouslySetInnerHTML}. The CSP is a defence-in-depth
measure for the unlikely case of a future regression.

\paragraph{Audit trail.} Every privileged write appends to
\texttt{audit\_logs}. The integrity dashboard renders the last 50 entries.
Together with the bcrypt hash, the JWT, and the role check, this gives
us a forensic chain that answers ``who changed which grade when''.

\paragraph{Residual risk and mitigations.}
\begin{itemize}[leftmargin=*]
  \item \textbf{Botnet with rotating IPs and headless browsers.} Could
        defeat rate limiting and IP-based anomaly heuristics.
        Mitigation: People's Choice exclusion still triggers if the same
        UA pattern reuses across sessions; CAPTCHA on
        \texttt{/votes/init} is a future-work item.
  \item \textbf{Local storage XSS exfiltration of JWT.} A successful XSS
        could read the token. Mitigation: short JWT lifetime,
        \texttt{JWT\_SECRET} rotatable to invalidate all tokens. Future
        work: move to httpOnly cookies.
  \item \textbf{Compromised admin account.} Same answer: rotate
        \texttt{JWT\_SECRET}, then issue new admin credentials.
\end{itemize}

\subsection{Scalability}

\paragraph{Stateless backend.} The Express process holds no per-user
session. Every request is independently authenticatable. Render's
autoscaler can multiply the number of instances without coordination.

\paragraph{Cache.} The LRU sits in front of every read endpoint with TTLs
chosen to balance freshness against load:

\begin{table}[ht]
  \centering
  \caption{Cache TTLs by key prefix.}
  \begin{tabular}{lll}
    \toprule
    Prefix & TTL & Invalidation events \\
    \midrule
    \texttt{projects:} & 60 s & vote, project create/update \\
    \texttt{winners:}  & 30 s & vote, grade submit \\
    \texttt{vote-counts} & 5 s & vote \\
    \texttt{admin:stats} & 10 s & none (TTL only) \\
    \bottomrule
  \end{tabular}
\end{table}

In a 10\,000-user load profile, the bulk of requests are gallery and
homepage reads. With a 60-second TTL the database sees one query per
filter combination per minute; the rest is L1 cache.

\paragraph{Atomic vote increment.} \texttt{rpc('increment\_vote\_count', \dots)}
runs an SQL \texttt{UPDATE projects SET vote\_count = vote\_count + 1
WHERE id = \$1}. Concurrent voters do not lose updates; we never
read-modify-write from Node.

\paragraph{Why we are not Redis-bound.} Process-local LRU is the right
tool for this scale. A second backend instance would have a separate
cache and slightly higher DB load; this is a $2\times$ degradation, not
a correctness bug. The cache module's API is small enough that swapping
in a Redis-backed implementation is a single-file change.

\paragraph{Frontend.} A 740\,kB JS bundle (217\,kB gzipped) is one HTTP
request to Vercel's edge. After the first paint, the SPA does not
reload; navigation is a route change. The bundle is large enough to
warrant code-splitting in a future iteration; we did not.

\subsection{Reliability}

\paragraph{Async error path.} \texttt{asyncHandler} wraps every async
controller; thrown errors and rejected promises both flow to the global
\texttt{errorHandler}, which logs with the request id and emits a JSON
response carrying the request id back to the client. The user can quote
that id when reporting a bug.

\paragraph{Logging.} Pino emits structured JSON logs in production and
pretty-prints in development. Every line carries a request id. The redact
list scrubs \texttt{authorization} headers, password fields, and tokens.

\paragraph{Submitted-grade immutability.} The \texttt{submitGrade}
controller refuses any write to a row whose status is
\texttt{submitted}. The audit log captures \emph{both} the new and the
previous total scores in metadata, so a later forensic pass can detect
out-of-band changes.

\paragraph{Failure isolation.}
\begin{itemize}[leftmargin=*]
  \item Anomaly persistence failure $\to$ logged at WARN, vote still counts.
  \item Audit insert failure $\to$ logged at WARN, the user-facing
        operation succeeds.
  \item AI API failure $\to$ deterministic stub returns same shape.
  \item SSE disconnect $\to$ watchdog reconnect plus polling fallback.
\end{itemize}

\subsection{Maintainability}

\paragraph{Clean separation.} The server is organised as
\texttt{routes / controllers / middleware / services / utils / config}.
The client mirrors this with \texttt{pages / components / context /
hooks / services / utils}. A new endpoint touches the smallest possible
set of files.

\paragraph{Linting.} The client uses ESLint with the React Hooks plugin;
the server uses a dedicated flat config (Listing~\ref{lst:eslint-server}).

\begin{lstlisting}[caption={\texttt{server/eslint.config.js}},label={lst:eslint-server}]
import js from '@eslint/js';
import globals from 'globals';

export default [
  js.configs.recommended,
  {
    languageOptions: {
      ecmaVersion: 2023, sourceType: 'module',
      globals: { ...globals.node },
    },
    rules: {
      'no-unused-vars': ['warn', { argsIgnorePattern: '^_', varsIgnorePattern: '^_' }],
      'no-console': 'off',
      'prefer-const': 'warn',
      eqeqeq: ['warn', 'smart'],
    },
    ignores: ['node_modules/**', 'seed/**'],
  },
];
\end{lstlisting}

\paragraph{Feature flags.} \texttt{REQUIRE\_VOTE\_TOKEN},
\texttt{ENABLE\_AI\_INSIGHTS}, and \texttt{VITE\_USE\_SSE} let us
disable the riskiest behaviour without a redeploy. This is the
maintenance equivalent of a circuit breaker.

\paragraph{Type-safety substitute.} We do not use TypeScript. We do use
zod, which gives runtime validation guaranteed at the boundary, plus
JSDoc-style types on the most-shared utilities. The trade-off is a
faster iteration loop at the cost of in-IDE autocomplete on internal
function calls.

\subsection{Availability}

\paragraph{Health probe.} \texttt{/api/health} pings Supabase and returns
DB latency, uptime, memory, cache stats, and the SSE client count. On
DB failure it returns \texttt{status: 'degraded'} with HTTP 200 so that
Render's health check does not flap; we still have a separate signal
(\texttt{db.ok}) for monitoring.

\paragraph{Graceful degradation.} The user-facing surface is
intentionally tolerant of failure modes:

\begin{itemize}[leftmargin=*]
  \item AI panel down $\to$ stub fills the same panel.
  \item SSE down $\to$ polling fallback fetches every 30\,s.
  \item Supabase down $\to$ cache serves the last successful read; new
        writes return clean 500 rather than partial state.
\end{itemize}

\paragraph{Recovery time.} Render's free-tier dyno restart is 5--15
seconds. The frontend continues to render whatever it has; on
reconnect, the SSE channel re-syncs the session state.

\subsection{Efficiency}

\paragraph{Read-path budget.} Cached reads are O(1) memory lookups.
On a cache miss, the project list is one query with one count and one
range. Winners is six queries, batched in two \texttt{Promise.all}
groups, totalling $\leq 50$\,ms in normal conditions.

\paragraph{Write-path budget.} A vote: 1 SELECT (project), 1 SELECT
(duplicate), 1 INSERT (vote), 1 RPC (counter), 1 in-memory broadcast,
3 cache invalidations, 1 best-effort flag insert. All synchronous I/O
in the hot path is to a single Supabase region.

\paragraph{Measured cache hit rate.} The
\texttt{/admin/analytics} page surfaces the live hit rate. After the
first 30\,seconds of an event with $\sim$150 simulated visitors the
hit rate stabilises in the 70--80\% band.

\paragraph{Bundle size.} 740\,kB minified, 217\,kB gzipped. We acknowledge
this is large for a primarily-mobile audience and treat it as
future-work (Section~\ref{sec:future}).
