\section{Deployment and Operations}
\label{sec:deploy}

\subsection{Topology}

\begin{itemize}[leftmargin=*]
  \item \textbf{Frontend:} Vercel project linked to the GitHub repo.
        Builds on push to \texttt{master}. \texttt{vercel.json} rewrites
        \texttt{/api/(.*)} to the Render origin so the SPA can use a
        same-origin API base URL.
  \item \textbf{Backend:} Render Web Service, Node 20 runtime,
        \texttt{npm start} as the entrypoint. Port 5001 inside the
        container.
  \item \textbf{Database:} Supabase project (us-east-1). Service-role key
        held only on Render.
  \item \textbf{LLM:} Anthropic API. Key held only on Render.
\end{itemize}

\subsection{Environment variables}

Table~\ref{tab:env} lists every variable read by the backend.

\begin{table}[ht]
  \centering
  \caption{Backend environment variables.}\label{tab:env}
  \begin{tabularx}{\linewidth}{lXl}
    \toprule
    \textbf{Variable} & \textbf{Purpose} & \textbf{Required?} \\
    \midrule
    \texttt{PORT}               & Listening port              & default 5001 \\
    \texttt{SUPABASE\_URL}      & Project URL                  & yes \\
    \texttt{SUPABASE\_SERVICE\_KEY} & Service-role key          & yes \\
    \texttt{JWT\_SECRET}        & HMAC secret for JWT signing  & yes \\
    \texttt{JWT\_EXPIRES\_IN}   & e.g.\ \texttt{7d}            & yes \\
    \texttt{NODE\_ENV}          & \texttt{production} on Render & rec. \\
    \texttt{LOG\_LEVEL}         & pino log level               & default info \\
    \texttt{CORS\_ORIGIN}       & origin allow list            & default \texttt{*} \\
    \texttt{REQUIRE\_VOTE\_TOKEN} & enforce HMAC vote tokens    & default false \\
    \texttt{VOTE\_TOKEN\_SECRET}& HMAC secret (falls back to \texttt{JWT\_SECRET}) & opt. \\
    \texttt{ANTHROPIC\_API\_KEY}& Claude key. Empty = stub mode & opt. \\
    \texttt{ANTHROPIC\_MODEL}   & override model id            & default \texttt{claude-haiku-4-5-20251001} \\
    \texttt{ENABLE\_AI\_INSIGHTS} & set to \texttt{false} to force stub & default true \\
    \bottomrule
  \end{tabularx}
\end{table}

Frontend variables (Vite reads anything prefixed \texttt{VITE\_}):

\begin{itemize}[leftmargin=*]
  \item \texttt{VITE\_API\_URL}; defaults to \texttt{/api}; override
        for direct backend calls in dev.
  \item \texttt{VITE\_USE\_SSE}; \texttt{true} (default) or
        \texttt{false} to fall back to polling.
\end{itemize}

\subsection{Migrations}

Apply, in order, the SQL files under \texttt{server/migrations/} via the
Supabase SQL editor. The current migration set is:

\begin{itemize}[leftmargin=*]
  \item \texttt{001\_audit\_logs.sql}
  \item \texttt{002\_vote\_flags.sql}
  \item \texttt{003\_ai\_insights.sql}
\end{itemize}

The original schema (\texttt{projects}, \texttt{judges},
\texttt{judge\_projects}, \texttt{votes}, \texttt{grades},
\texttt{schedule\_items}, \texttt{live\_sessions}) was created out-of-band
during initial setup and is reproduced in
Appendix~\ref{app:schema}.

\subsection{Seeding}

\texttt{npm run seed} populates 24 projects, 5 TED talks, 6 interviews,
5 judges, the schedule, and a single \texttt{live\_sessions} row keyed
\texttt{main}. The seed script is idempotent: it clears the relevant
tables first.

\subsection{Show-day runbook}

The runbook lives in \texttt{docs/runbook.md}. The summarised checklist
is:

\begin{enumerate}[leftmargin=*]
  \item Pull latest, redeploy if there were changes.
  \item Apply any new migrations.
  \item Run \texttt{npm run seed}.
  \item Optionally pre-warm AI insights:
        \texttt{node server/scripts/precacheInsights.js}.
  \item Open \texttt{/admin/integrity} and \texttt{/admin/analytics} in
        admin browser tabs.
  \item Toggle \texttt{set-public} to true at start; flip
        \texttt{voteCountVisible} per discretion.
  \item During event, watch the integrity dashboard for high-severity
        flags. If a project is unfairly tainted, an admin can
        \texttt{DELETE FROM vote\_flags WHERE project\_id = ?} via the
        Supabase SQL editor.
  \item After event, optionally lock the platform back to private.
\end{enumerate}

\subsection{Observability}

Pino emits NDJSON in production. We do not currently ship a hosted log
collector, but Render's web UI exposes log tailing per dyno. Adding a
hosted collector (Better Stack, Logtail, Datadog) is one
\texttt{pino-transport} line change.

The \texttt{/admin/analytics} page doubles as a low-fidelity ops
dashboard; the cache hit rate and submitted-grade count are the two
metrics we glance at during a live event.

\subsection{Disaster recovery}

\begin{itemize}[leftmargin=*]
  \item \textbf{Lost JWT secret.} Rotate by changing
        \texttt{JWT\_SECRET} on Render and restarting; all judges
        re-login.
  \item \textbf{Compromised admin account.} Same answer + \texttt{UPDATE
        judges SET password = bcrypt-of-new-password WHERE email = '...'}.
  \item \textbf{Render outage.} Frontend continues to render the last
        cached state. Voting and grading fail with 5xx; clients can
        retry. We accept this as the cost of free-tier hosting; a paid
        tier with multi-region failover is a future-work item.
  \item \textbf{Supabase outage.} \texttt{/api/health} returns
        \texttt{degraded}. Reads served from cache for the next
        TTL window. Writes fail.
  \item \textbf{Anthropic outage.} AI panel falls back to stub silently;
        public surfaces unaffected.
\end{itemize}
