\section{Limitations and Future Work}
\label{sec:future}

\subsection{Honest limitations}

\begin{itemize}[leftmargin=*]
  \item \textbf{No automated test suite.} The architecture supports
        testing, but tests do not yet exist. Adding Vitest unit tests for
        the pure utilities (\texttt{verifyVoteToken},
        \texttt{scoreVote}) and integration tests for the four flows
        would close the biggest single gap.
  \item \textbf{Single-region deploy.} Render dyno is in one region;
        Supabase project is in one region. A regional outage takes the
        platform down. Multi-region read replicas are a Supabase Pro
        feature.
  \item \textbf{Process-local cache and SSE state.} Both are
        per-instance. Scaling out to multiple instances requires Redis
        for cache coherence and Redis pub/sub for SSE fan-out.
  \item \textbf{No CAPTCHA or hCaptcha on \texttt{/votes/init}.}
        A determined attacker with a botnet can still issue an init token
        per attacker browser. The anomaly detector raises the cost, but
        does not eliminate it.
  \item \textbf{JWT in localStorage.} An XSS would expose the token. The
        modern preference is httpOnly cookies; we deferred the change to
        avoid the CSRF-token plumbing it would require.
  \item \textbf{Bundle size.} 740\,kB unsplit. Acceptable on Wi-Fi,
        slow on a cellular connection.
  \item \textbf{No internationalisation.} The UI has stubs for
        English/Arabic but not all strings are wired through the
        translator.
  \item \textbf{Single-event tenancy.} The \texttt{live\_sessions.key
        = 'main'} pattern works for one event; supporting parallel
        events would require schema changes.
\end{itemize}

\subsection{Future work, prioritised}

\subsubsection*{Tier 1; next iteration}

\begin{enumerate}[leftmargin=*]
  \item \textbf{Vitest test suite.} Unit + integration. Target:
        80\% statement coverage on \texttt{server/}.
  \item \textbf{Code-splitting.} Use React Router's lazy routes. Cuts
        initial bundle by an estimated 60\%.
  \item \textbf{httpOnly cookie auth.} Move JWT to a secure cookie;
        add a CSRF token to mutating endpoints.
  \item \textbf{hCaptcha on \texttt{/votes/init}.} Closes the last
        residual security gap for anonymous voting.
\end{enumerate}

\subsubsection*{Tier 2; if scope grows}

\begin{enumerate}[leftmargin=*]
  \setcounter{enumi}{4}
  \item \textbf{Multi-event tenancy.} Add an \texttt{events} table; key
        every domain row by \texttt{event\_id}; rewrite
        \texttt{live\_sessions} to be (\texttt{event\_id}, key).
  \item \textbf{Redis-backed cache + pub/sub.} Swap \texttt{utils/cache.js}
        and \texttt{services/eventBus.js} behind their existing APIs.
  \item \textbf{i18n.} Wire \texttt{LanguageContext.jsx} through every
        text block; add Arabic translations for every key.
  \item \textbf{Voter accounts.} Optional Magic-link auth for the
        audience to lift the anonymous-voting integrity ceiling.
\end{enumerate}

\subsubsection*{Tier 3; speculative}

\begin{enumerate}[leftmargin=*]
  \setcounter{enumi}{8}
  \item \textbf{LLM-assisted feedback summarisation.} After all judges
        submit, summarise their feedback into a single per-project
        narrative for the team to receive.
  \item \textbf{Live transcription.} Run pitch audio through Whisper
        and present a real-time caption track for accessibility.
  \item \textbf{Mobile-native app.} React Native or Capacitor wrapper
        of the existing SPA, with a Push Notification track for
        ``your assigned project is up next''.
  \item \textbf{Anomaly detector ML upgrade.} Replace the rule-based
        scorer with a small classifier trained on historical
        flagged/clean votes. Only worth doing once we have $\geq$10
        events of historical data.
\end{enumerate}

\subsection{Lessons learned}

\begin{itemize}[leftmargin=*]
  \item \textbf{Defence in depth is a multiplier, not a tax.} Each
        single defence (rate limit, HMAC token, anomaly detector) is
        easy to build. The combined effect dominates any single defence
        we could have built more carefully.
  \item \textbf{Boring tech buys time for interesting tech.} React +
        Express + Postgres is unfashionable; that left budget for the
        AI panel and the real-time push.
  \item \textbf{Free tiers are political acts.} Vercel, Render, and
        Supabase offering a real production runtime for free changes
        what a single student can ship.
  \item \textbf{Logs are infrastructure.} The decision to add structured
        logging early (with request ids) paid back during every
        debugging session that followed.
\end{itemize}
