\section*{References}
\addcontentsline{toc}{section}{References}
\label{sec:refs}

\begin{thebibliography}{99}

  \bibitem{w3c-sse}
    W3C, \emph{Server-Sent Events (W3C Recommendation)},
    \url{https://www.w3.org/TR/eventsource/}, 2015.

  \bibitem{leiba-spam}
    B. Leiba, \emph{The IETF Anti-Spam Effort and the Layered Defense Principle},
    Proc.\ IETF, 2009.

  \bibitem{burstein-llm}
    J. Burstein et al., \emph{Using Large Language Models in Educational
    Assessment: Promise and Perils}, ETS Research Report Series, 2024.

  \bibitem{anthropic-cache}
    Anthropic, \emph{Prompt Caching; API Documentation},
    \url{https://docs.anthropic.com/en/docs/build-with-claude/prompt-caching}, 2025.

  \bibitem{helmet}
    \texttt{helmetjs}, \emph{Helmet; Express middleware for HTTP security
    headers}, \url{https://github.com/helmetjs/helmet}, 2024.

  \bibitem{erl}
    N. Walsh et al., \emph{express-rate-limit},
    \url{https://github.com/express-rate-limit/express-rate-limit}, 2024.

  \bibitem{lru-cache}
    I. Z. Schlueter, \emph{lru-cache},
    \url{https://github.com/isaacs/node-lru-cache}, 2024.

  \bibitem{pino}
    M. Collina et al., \emph{pino; very low overhead Node.js logger},
    \url{https://github.com/pinojs/pino}, 2024.

  \bibitem{zod}
    C. Bond, \emph{Zod: TypeScript-first schema validation with static
    type inference}, \url{https://zod.dev}, 2024.

  \bibitem{recharts}
    Recharts contributors, \emph{Recharts; a composable charting
    library built on React components},
    \url{https://recharts.org}, 2024.

  \bibitem{owasp-top10}
    OWASP, \emph{OWASP Top Ten Web Application Security Risks},
    \url{https://owasp.org/Top10/}, 2021.

  \bibitem{nielsen-ux}
    J. Nielsen, \emph{Response Times: The 3 Important Limits},
    Nielsen Norman Group, 1993.

  \bibitem{fielding-rest}
    R. T. Fielding, \emph{Architectural Styles and the Design of
    Network-based Software Architectures}, PhD thesis, UC Irvine, 2000.

  \bibitem{nist-csf}
    NIST, \emph{Cybersecurity Framework v1.1},
    NIST CSF, 2018.

\end{thebibliography}
